---
title: "hw04-MDS"
author: "Weiting Gu"
date: "2018Äê10ÔÂ12ÈÕ"
output:   
  html_document:
    keep_md: true
---
## 1. Functions in the R Base Package
#### a. Which base function has the longest name
```{r,warning = FALSE, message=FALSE}
# install.packages("RJSONIO")
# install.packages("purrr")
library(RJSONIO)
library(purrr)
content <- mget(ls("package:base"), inherits = TRUE)
base_functions <- Filter(is.function, content)
names1 <- names(base_functions)
namelength<-map(names1,nchar)
namelength<-unlist(namelength)
names1[match(max(namelength),namelength)]
```

#### b. Which base function has the most arguments
```{r,warning = FALSE, message=FALSE}
bf <- map(base_functions,safely(formals))
bf2 <- transpose(bf)$result
bf3 <- map(bf2,length)
bf3 <- unlist(bf3)
names1[match(max(bf3),bf3)]
```

#### c. How many base functions have no arguments

```{r,warning = FALSE, message=FALSE}
bf4 <- map(bf2,length)
length(which(bf4 == 0))
```
These functions are quite primitive. They themselves could express certain meanings (such as relationship, direction, etc.) without requiring any other variables, conditions or constraints.


## 2. Infant Mortality and GPD per Capita
#### a. infant mortality rates
5 highest infant mortality rates in 2017
```{r,warning = FALSE, message=FALSE}
# install.packages("WDI")
library(WDI)
WDI <- WDI(country = "all", indicator = c("NY.GDP.PCAP.PP.KD","SP.DYN.IMRT.IN"),start = 1960,
  end = 2017, extra = TRUE, cache = NULL) 
names(WDI)[names(WDI)=="NY.GDP.PCAP.PP.KD"]="gdpcap"
names(WDI)[names(WDI)=="SP.DYN.IMRT.IN"]="infmort"
library(dplyr)
WDI2 <- WDI %>%
  filter(WDI$region!="Aggregates") %>%
  filter(year==2017) 
WDI3 <- WDI2 %>%
  arrange(desc(infmort)) %>%
  dplyr::select(country,gdpcap)%>%
  head(5)
WDI3
```

5 lowest infant mortality rates in 2017
```{r,warning = FALSE, message=FALSE}
WDI4 <- WDI2 %>%
  arrange(infmort) %>%
  dplyr::select(country,gdpcap)%>%
  head(5)
WDI4
```

#### b. Overall regression
```{r,warning = FALSE, message=FALSE}
reg <- lm(infmort~gdpcap,data = WDI2)
summary(reg)
plot(WDI2$gdpcap,WDI2$infmort,main = "overall regression predicting infant mortality from GDP per capita",xlab="GDP per capita",ylab="infant mortality")
abline(reg)
```


There is a negative correlation between infant mortality and GDP per capita across countries. The higher GDP per capita, the lower infant mortality.

#### c. Regression coefficient estimates by region, sorted
```{r,warning = FALSE, message=FALSE}
options(scipen = 1000)
WDI5 <- WDI %>%
  filter(WDI$region!="Aggregates") 
WDI6 <- WDI5 %>%
  filter(is.na(gdpcap)!= TRUE)%>%
  filter(is.na(infmort)!=TRUE)

WDI7 <- WDI6 %>%
  split(WDI6$region)
WDI8<- WDI7[-1]
model <- map(WDI8,~lm(infmort ~ gdpcap, data =.,na.rm=TRUE)) %>%
  map(~ coef(.)) %>%
  map_dbl("gdpcap") %>%
  sort()
as.table(model)
```

#### d. Regression by country
Percentage of positive relationship
```{r,warning = FALSE, message=FALSE}

WDI9 <- WDI6 %>%
  split(WDI6$country)
WDI10<- WDI9[-1]
model2 <- map(WDI10,~lm(infmort ~ gdpcap, data =.))%>%
  map(coefficients) %>%
  map_dbl("gdpcap") 
nameslist <-names(model2[model2>0])
nameslist2 <- nameslist[is.na(nameslist)==FALSE]


modelframe <- map(WDI10,~lm(infmort ~ gdpcap, data =.))%>%
  map(summary)%>%
  map(~ coef(.)) 
sig <- modelframe[nameslist2] %>%
  as.data.frame()
sig1 <- sig[2,]%>%
  dplyr::select(contains("Pr...t..")) 
number<-length(sig1[sig1<0.05])
percentage <- number/length(modelframe)
paste(round(percentage,3)*100, "%", sep='')
```

Histogram of the slope coefficients


```{r,warning = FALSE, message=FALSE}

allcoef <- map(WDI10,~lm(infmort ~ gdpcap, data =.,na.rm=TRUE)) %>%
  map(~ coef(.)) %>%
  map_dbl("gdpcap")

hist(allcoef, main = "histogram of the slope coefficients")
```


Which countries are most at odds with the overall regression?
```{r,warning = FALSE, message=FALSE}
modelframe2 <- map(WDI10,~lm(infmort ~ gdpcap, data =.))%>%
  map(summary)%>%
  map(~ coef(.)) %>%
  as.data.frame() %>%
  dplyr::select(contains("Estimate"))
number <- match(max(allcoef,na.rm=TRUE),modelframe2[2,])
names(WDI10[number])
number <- match(min(allcoef,na.rm=TRUE),modelframe2[2,])
names(WDI10[number])

```

#### e. Added squared term
Average adjusted r squared, when not adding a squared term
```{r,warning = FALSE, message=FALSE}
model3 <- map(WDI10,~lm(infmort ~gdpcap+I(gdpcap^2), data =.))%>%
  map(summary)%>%
  map_dbl("adj.r.squared")
model4 <- map(WDI10,~lm(infmort ~ gdpcap, data =.))%>%
  map(summary)%>%
  map_dbl("adj.r.squared")

model6 <- model4[model4>0]
sum(model6)/length(WDI10)

```

Average adjusted r squared, when adding a squared term
```{r,warning = FALSE, message=FALSE}
model5 <- model3[model3>0]
sum(model5)/length(WDI10)
```

We can see that when adding a squared term (square of gdpcap), the adjusted r squared increases a lot. I would recommend to keep the squared term to make the model fit more.

